Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-02-28 Manuscript/manuscript.Rmd
manuscript edits

3. **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated. The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1-8).

@@

When assessing the collinearity of the genomic annotations, it was found that the total number of bases that the number overlapped bases between genomic bins flanked by a TAD boundary were highly correlated between many genomic annotations (). That is, many genomic annotations tended to colocalize near eachother at the boarders of domains. This was present across both resolution and cell line. Specifically, we found that the CTCF, Rad21, Smc3ab, and Znf143 transcription factor binding sites were highly colocalized near TAD boundaries. Likewise, many histone modifications also tended to appear near TAD boundaries in conjunction with one another including H3K4me1, H3K4me2, H3K4me3, H3K9ac, and H3K27ac. Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated with on another, yet inversely correlated with many transcription factor binding sites. The high correlations among many of the genomic annotations gives precedent for the use of an elastic-net regularization.

>>>>

3. **Log2 Distance**: For each genomic bin, the $log_{2}$ of the distance in bases (refered to hereafter simply as $\textit{distance}$), from the center of the bin to the center of the nearest region defined by a specific genomic annotation was calculated. The log transformation was used as a normalization technique in order to account for the skewness of the data (Supplementary Figures 1).

@@

When assessing the collinearity of the genomic annotations, it was found that the total number of bases that the number overlapped bases between genomic bins flanked by a TAD boundary were highly correlated between many genomic annotations (Supplementary Figure 2). That is, many genomic annotations tended to colocalize near eachother at the boarders of domains. This was present across both resolution and cell line. Specifically, we found that the CTCF, Rad21, Smc3ab, and Znf143 transcription factor binding sites were highly colocalized near TAD boundaries. Likewise, many histone modifications also tended to appear near TAD boundaries in conjunction with one another including H3K4me1, H3K4me2, H3K4me3, H3K9ac, and H3K27ac. Furthermore, particular chromatin segmentation states, inclduing heterochromatin, repressed chromatin, poised promotors, and repetitive copy number variations, were found to be highly correlated with on another, yet inversely correlated with many transcription factor binding sites. The high correlations among many of the genomic annotations gives precedent for the use of an elastic-net regularization.
